### 2008-08-19 doc/storage_system/arc1-storage-documentation.tex
Rename arc_storage_cli.py arc_storage_cli

In the first prototype release there is one client tool called \verb!arc_storage_cli.py!, which is written in Python, and only need a basic Python installation to run. It is capable of communicating with a given Bartender service, and uploading and downloading TURLs via HTTP.

The methods can be listed with:
\begin{verbatim}
$ arc_storage_cli.py
Usage:
  arc_storage_cli.py <method> [<arguments>]
Supported methods: stat, make[Collection], unmake[Collection], list, move,
    put[File], get[File], del[File]
\end{verbatim}
Without arguments, each method prints its own help:
\begin{verbatim}
$ arc_storage_cli.py move
Usage: move <sourceLN> <targetLN>
\end{verbatim}

@@

\begin{verbatim}
$ cat testfile 
This is a testfile.
$ arc_storage_cli.py put testfile /tmp/
- The size of the file is 20 bytes
- The md5 checksum of the file is 9a9dffa22d227afe0f1959f936993a80
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's putFile method...
- done in 0.08 seconds.
- Got transfer URL: http://localhost:60000/httpd/d15900f5-34ee-4bba-bb10-73d60d1c0d75
- Uploading from 'testfile'
    to 'http://localhost:60000/httpd/d15900f5-34ee-4bba-bb10-73d60d1c0d75' with http...
Uploading 20 bytes... data sent, waiting... done.
- done in 0.0042 seconds.
'testfile' (20 bytes) uploaded as '/tmp/testfile'.
$ arc_storage_cli.py stat /tmp/testfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
$ arc_storage_cli.py get /tmp/testfile newfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's getFile method...
- done in 0.05 seconds.
- Got transfer URL: http://localhost:60000/httpd/dab911d0-110f-468e-b0c3-627af6e3af31
- Downloading from 'http://localhost:60000/httpd/dab911d0-110f-468e-b0c3-627af6e3af31'
    to 'newfile' with http...
Downloading 20 bytes... done.
- done in 0.0035 seconds.
'/tmp/testfile' (20 bytes) downloaded as 'newfile'.
$ cat newfile 
This is a testfile.
\end{verbatim}

>>>>

In the first prototype release there is one client tool called \verb!arc_storage_cli!, which is written in Python, and only need a basic Python installation to run. It is capable of communicating with a given Bartender service, and uploading and downloading TURLs via HTTP.

The methods can be listed with:
\begin{verbatim}
$ arc_storage_cli
Usage:
  arc_storage_cli <method> [<arguments>]
Supported methods: stat, make[Collection], unmake[Collection], list, move,
    put[File], get[File], del[File]
\end{verbatim}
Without arguments, each method prints its own help:
\begin{verbatim}
$ arc_storage_cli move
Usage: move <sourceLN> <targetLN>
\end{verbatim}

@@

\begin{verbatim}
$ cat testfile 
This is a testfile.
$ arc_storage_cli put testfile /tmp/
- The size of the file is 20 bytes
- The md5 checksum of the file is 9a9dffa22d227afe0f1959f936993a80
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's putFile method...
- done in 0.08 seconds.
- Got transfer URL: http://localhost:60000/httpd/d15900f5-34ee-4bba-bb10-73d60d1c0d75
- Uploading from 'testfile'
    to 'http://localhost:60000/httpd/d15900f5-34ee-4bba-bb10-73d60d1c0d75' with http...
Uploading 20 bytes... data sent, waiting... done.
- done in 0.0042 seconds.
'testfile' (20 bytes) uploaded as '/tmp/testfile'.
$ arc_storage_cli stat /tmp/testfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
$ arc_storage_cli get /tmp/testfile newfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's getFile method...
- done in 0.05 seconds.
- Got transfer URL: http://localhost:60000/httpd/dab911d0-110f-468e-b0c3-627af6e3af31
- Downloading from 'http://localhost:60000/httpd/dab911d0-110f-468e-b0c3-627af6e3af31'
    to 'newfile' with http...
Downloading 20 bytes... done.
- done in 0.0035 seconds.
'/tmp/testfile' (20 bytes) downloaded as 'newfile'.
$ cat newfile 
This is a testfile.
\end{verbatim}
